Forecasting the age structure of the scientific workforce in Australia

### 2025-12-01 response.qmd

We assume the age distribution of graduates is a product of age-dependent and time-dependent variables, $g_x$ and $G_{i,t}$. Primarily, this is a pragmatic choice because we do not have more detailed data available. We can get age distributions of graduates across all disciplines in Australia, but not for each discipline; and we can get the numbers of graduates by discipline and year in Australia, but with no age breakdown.  The most likely consequence of this simplifying assumption is that the variability in graduate numbers by age and time could be underestimated. It is conceivable that older graduates are drawn to different disciplines than younger graduates, or that fashionable disciplines change over time, resulting in different age distributions of the graduates over time. But without specific data related to this issue, we can only speculate. In any case, the comment above regarding the remainder term is also relevant here.

We have added a new paragraph in Section 2 along these lines.

::: {.reviewer}
3. The authors mentioned that the remainder includes large positive and negative fluctuations caused by international students returning to their home countries after graduation, as well as complex economic behaviors involving career changes and international migration. Strictly speaking, are these macroeconomic and social trends ($E_{i,x,t}$) thought to be long-term stationary? It is recommended that the discussion take into account that the stationarity assumption will fail if major policy or global economic structural changes take place, and this is a significant factor in forecasting uncertainty.
:::

We do not assume that the remainder term is stationary. We used stationary ARMA processes for the corresponding principal component scores because they all were found to be stationary using KPSS tests, with a Bonferonni adjustment due to the use of multiple tests. The code for these tests can be found in the file `extra_code/stationary.R` in the GitHub repository. But there is no reason why the principal component scores could not be modelled using non-stationary processes if the data supported it. In particular, if major policy or global economic structural changes took place, this is likely to lead to non-stationarity in the remainder term, leading to greater forecast uncertainty.
